### 2024-06-03 ms.qmd
Updates

---
docx: 
bibliography: "./bib/refs.bib"
csl: "./bib/animal-cognition.csl"
reference-doc: "./bib/tmpl.docx"
execute:
  echo: false
  error: false
  cache: false
  warning: false
link-citations: true
crossref:  
  fig-title: Fig    # (default is "Figure")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Table  # (default is "Table")
editor_options: 
  chunk_output_type: console
---

@@

Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth]. These cognitive processes underpin animal foraging, mate choice, antipredatory strategies and social behaviours that are crucial for the survival and reproduction [@dukas_evolutionary_2004]. Learning - the acquisition of new information [@dukas_evolutionary_2004] - is fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013]. However, in nature, there is individual variation in the capacity to acquire new information, depending on factors like age, sex, gut microbiota, or the environment where organisms develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning]. The latter can be particularly relevant since the brain is especially susceptible to environmental conditions during early stages of development [@zhu_prenatal_2004]. Therefore, investigating the effects of the developmental environment on learning can be essential to understand how individual variation in learning is shaped, and, in consequence, to predict animals' responses towards environmental change.

In this sense, prenatal glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020]. For instance, some studies have demonstrated that prenatal stress and high prenatal GC levels impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors like sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016]. Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020]. In fact, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@dayananda_incubation_2017; @abayarathna_effects_2020]. In this vein, the effects of prenatal temperature and GCs are linked to similar alterations in neural structure and metabolic activity [@coomber_independent_1997; @lemaire_prenatal_2000; @sakata_neural_2000; @zhu_prenatal_2004; @du_dynamic_2009; @amiel_effects_2017; @beltran_are_2021], which suggests that bot factors may interact to shape learning [@noble_developmental_2018]. Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs. However, our understanding of how these two factors interact remains incomplete.

In this study, we aim to explore the interactive effects between prenatal GCs and the prenatal thermal environment on learning. We utilized two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_), as model species. We experimentally increased corticosterone (CORT) - the main GC in birds, reptiles, amphibians, and rodents [@Crino_2023] - levels in the eggs of these two species of skinks and then incubated them at two different temperatures in a 2X2 factorial design. Post-incubation, the juveniles were subjectd to a colour-associative task to assess their learning abilities. Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's physiology that will ultimately impact learning skills. We predict that individuals exposed to high levels of CORT and/or low temperatures will perform less proficiently compared to control individuals or those exposed to high temperatures. Additionally, we anticipate that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning. This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures accelerates the metabolism of CORT, resulting in embryos being exposed to CORT for a shorter time. Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species when tested in an associative learning task [@bezzina2014does].

@@

#### Subjects  
_L. guichenoti_ and _L. delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011]. Both species have similar breeding periods, but with some differences in reproductive output: while *L. delicata* lays 1 to 6 eggs in only one clutch per season, *L. guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season [@chapple_know_2011; @chapple_biology_2014]. Also, some sudies have found some behavioural divergence between the two skinks [@chapple_know_2011]. _L. delicata_ is more exploratory and bolder than _L. guichenoti_ [@chapple_know_2011] which was related to the former's success as an invassive species [@chapple_know_2011; @bezzina2014does], but not with their ability to learn in an associatve learning task [@bezzina2014does].

@@

#### Statistical analyses  
We performed the analyses with species (_L. delicata_ or _L. guichenoti_) separately. We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour (blue or red) as well. As such, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022). Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations. 'Choice', i.e. whether the feeder visited first was the correct one (1) or not (0) was used as the response variable. The fixed effects of the model included a triple interaction between: 'Trial' as a nummeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors. For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the 'Trial' within each level of lizard identity.  
We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned. More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not. We used the pmcmc method to test whether those slopes or the comparissons between treatments (e.g. slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

@@

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @fig_deli and @fig-guich.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id) + (1| clutch)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = FALSE)
write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = FALSE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = FALSE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = FALSE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

@@

We found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to slopes of individuals assigned to the group 'Red' for _L. delicata_ ('Blue' mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`), but not for _L. guichenoti_ ('Blue' mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`). However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and @fig-results) that could be affecting the estimated slopes. As such, we analysed the between treatments differences for each group separately.

For those _L. delicata_ assigned to group 'Red', we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (**FIG**). Similarly, those assigned to 'Blue' were not afected by CORT (Control - CORT = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (**FIG**).

```{r, fig-deli}
#| label: fig-deli
#| fig.cap: "Results for Lampropholis delicata for both colour groups "red" (A,B) and "blue" (C, D). Panels A and C show the predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions. The different colours indicate the different treatments. Panels B and D show the distribution of the estimates of slopes per each treatment. The x-axis represents the slope estimate, and in the y-axis are the density of the estimates. The different colours indicate the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# First step, create the dfs for all models
## Red
fig_dar_AC_df <- df_plotAC("deli_red")
fig_dar_BD1_df <- df_plotBD1("deli_red")
fig_dar_BD2_df <- df_plotBD2("deli_red")
## Blue
fig_dab_AC_df <- df_plotAC("deli_blue")
fig_dab_BD1_df <- df_plotBD1("deli_blue")
fig_dab_BD2_df <- df_plotBD2("deli_blue")
#
# Second step, create the plots
fig_dar <- plotting(sp = "deli", col = "red", df_prob = fig_dar_AC_df, df_violin = fig_dar_BD1_df, df_points = fig_dar_BD2_df)
fig_dab <- plotting(sp = "deli", col = "blue", df_prob = fig_dab_AC_df, df_violin = fig_dab_BD1_df, df_points = fig_dab_BD2_df)
#
# Third step, merge plots
fig_deli <- plot_grid(fig_dar, fig_dab, ncol = 1) +
  theme(plot.margin = margin(1, 1, 1.5, 1, "cm")) +
  annotate("text", x = 0.5, y = 0.985, label = "Lampropholis delicata", size = 4.5, color = "black", fontface = "italic")
ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/fig_deli.png")
```

>>>>

---
docx: "Early environmental conditions do not impact associative learning in two species of skink"
bibliography: "./bib/refs.bib"
csl: "./bib/animal-cognition.csl"
reference-doc: "./bib/tmpl.docx"
execute:
  echo: false
  error: false
  cache: false
  warning: false
link-citations: true
crossref:  
  fig-title: Fig    # (default is "Figure")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Table  # (default is "Table")
editor_options: 
  chunk_output_type: console
---

@@

Cognition is defined as the processes by which animals gather, preserve, and use information from their environment through perception, learning, memory, and decision making [@shettleworth]. These cognitive processes underpin animal foraging, mate choice, antipredatory strategies and social behaviours that are crucial for survival and reproduction [@dukas_evolutionary_2004]. Learning - the acquisition of new information [@dukas_evolutionary_2004] - is fundamental for coping with environmental changes by enabling individuals to create new associations between events [@dukas_evolutionary_2004; @leal_behavioural_2012; @buchanan_condition_2013]. However, in nature, there is individual variation in the capacity to acquire new information, depending on factors like age, sex, gut microbiota, or the environment where organisms develop [@szuran_water_1994; @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @carazo_sex_2014; @noble_age-dependent_2014; @alemohammad_2022_microbiota_learning]. The latter can be particularly relevant since the brain is especially susceptible to environmental conditions during early stages of development [@zhu_prenatal_2004].Understanding how the environment shapes learning processes is essential due to its profound impact on animals' fitness and adaptability to environmental changes.

In this context, the prenatal environment emerges as a relevant key of animals' cognitive skills, shaping their capacity for learning and adaptation. Prenatal glucocorticoids (GCs) - hormones related to organisms' response to stress [@sapolsky_how_2000] - and prenatal thermal environment are known to influence learning abilities in different taxa [see @lemaire_prenatal_2000; @zhu_prenatal_2004; @amiel_hotter_2012; @amiel_egg_2014; @crino_corticosterone_2014; @abayarathna_effects_2020]. For instance, some studies have demonstrated that prenatal stress and high prenatal GC levels impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @farrell_developmental_2015-learn], while others showed diverse effects depending on factors like sex or the nature of the learning task [@szuran_water_1994; @crino_corticosterone_2014-learn; @farrell_developmental_2015-learn; @bebus_associative_2016]. Similarly, some experiments have shown significant impacts of prenatal temperature on learning in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @dayananda_incubation_2017; @abayarathna_effects_2020]. In fact, high incubation temperatures have been linked with faster learning rates in skinks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014], while velvet geckos incubated at temperatures over their natural range learn slower than those incubated within the natural thermal limits [@dayananda_incubation_2017; @abayarathna_effects_2020]. In this vein, the effects of prenatal temperature and GCs are linked to similar alterations in neural structure and metabolic activity [@coomber_independent_1997; @lemaire_prenatal_2000; @sakata_neural_2000; @zhu_prenatal_2004; @du_dynamic_2009; @amiel_effects_2017; @beltran_are_2021], which suggests that bot factors may interact to shape learning [@noble_developmental_2018]. Furthermore, GCs can play an pivotal role in determining vertebrate responses to elevated temperatures [@Crino_2023] potentially fostering natural interactions between temperature and GCs. However, our understanding of how these two factors interact remains incomplete.

In this study, we aim to explore the interactive effects between prenatal GCs and the prenatal thermal environment on learning. We utilized two species of skinks, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_), as model species. We experimentally increased corticosterone (CORT) - the main GC in reptiles [@Crino_2023] - in the eggs and then incubated them at two different temperatures in a 2X2 factorial design. Post-incubation, the juveniles were subjectd to a colour-associative task to assess their learning abilities. Our hypothesis posits that changes in CORT levels and temperature during early development will induce sustained effects on brain's physiology that will ultimately impact learning skills. We predicted that individuals exposed to high levels of CORT or low temperatures will perform less proficiently compared to control individuals or those incubated at higher temperatures. Additionally, we predicted that incubation at high temperatures will mitigate the impact of CORT on skink performance, while cold incubation temperatures are expected to enhance the detrimental effects of CORT on learning. This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures can accelerate CORT metabolism, resulting in embryos being exposed to CORT for a shorter time. Finally, we expect that the effects of the treatments will be similar in both species, as both species share similar life history traits and are closely related [@chapple_know_2011; @chapple_biology_2014], and other cognitive studies have not found any difference between species when tested in an associative learning task [@bezzina2014does].

@@

#### Subjects  
_L. guichenoti_ and _L. delicata_ are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia [@chapple_know_2011]. Both species have similar breeding periods, but with some differences in reproductive output: while *L. delicata* lays 1 to 6 eggs in only one clutch per season, *L. guichenoti* clutches are smaller (1-5 eggs per clutch) and they usually lay two clutches per season [@chapple_know_2011; @chapple_biology_2014]. Also, some sudies show behavioural differences between both skinks; _L. delicata_ is bolder and tends to explore more than _L. guichenoti_ [@chapple_know_2011]. These differences have been associated with _L. delicata_'s success as an invassive species [@chapple_know_2011; @bezzina2014does], but not with their ability to perform an associatve learning task [@bezzina2014does].

@@

#### Statistical analyses  
We performed the analyses for species separately. Because preliminary analyses showed a significant effect of the colour assigned, we decided to split the data by colour (blue or red). As such, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022). We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations. We employed correct choice [correct (1) or not (0)] as the response variable, and trial, incubation temperature (Cold versus Hot), hormone (CORT versus Control), and their interaction as fixed factors. We included a random intercept and slope (trial) for each lizard in our models. We also incorporated the clutch identity as a random factor. Since learning in lizards can be age-dependent [@noble_age-dependent_2014], and given that incubation temperature can affect hatching time, we explored the effects of age on learning. Lizards’ age at the beginning of the experiment ranged from 41 to 148 days old in _L. delicata_ and 48 to 132 in _L. guichenoti_. However, when this variable was included in the models we did not find any significant effect of age (see Supplementary material). As such, we present models without age as a fixed effect. We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species. Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments. Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not. We calculated the probability that slopes or contrasts between slopes differed from zero (p~mcmc~) using the posterior distributions. We considered statistical significance if p~mcmc~ < 0.05.

@@

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are listed in @fig_deli and @fig-guich.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id) + (1| clutch)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = FALSE)
write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = FALSE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = FALSE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = FALSE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

@@

We found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to slopes of individuals assigned to the group 'Red' for _L. delicata_ ('Blue' mean learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot)) - mean(c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(dab_CORTCold, dab_ControlCold, dab_CORTHot, dab_ControlHot) - c(dar_CORTCold, dar_ControlCold, dar_CORTCold, dar_ControlHot)), 3)`), but not for _L. guichenoti_ ('Blue' mean learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)), 3)`, 95% CI = [`r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot), 0.975), 3)`]; 'Red' mean learning slope = `r format_dec(mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, 95 CI = [`r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.025), 3)` , `r format_dec(quantile(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot), 0.975), 3)`]; 'Blue' learning slope - 'Red'learning slope = `r format_dec(mean(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot)) - mean(c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`, p~mcmc `r format_p(pmcmc(c(gab_CORTCold, gab_ControlCold, gab_CORTHot, gab_ControlHot) - c(gar_CORTCold, gar_ControlCold, gar_CORTCold, gar_ControlHot)), 3)`). However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material) that could be affecting the estimated slopes. As such, we analysed the between treatments differences for each group separately.

For those _L. delicata_ assigned to group 'Red', we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(dar_ControlCold - dar_ControlHot)) - mean(c(dar_CORTCold, dar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dar_ControlCold - dar_ControlHot) - c(dar_CORTCold, dar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dar_ControlHot, dar_CORTHot)) - mean(c(dar_ControlCold, dar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dar_ControlHot, dar_CORTHot) - c(dar_ControlCold, dar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dar_ControlHot - dar_CORTHot) - mean(dar_ControlCold - dar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dar_ControlHot - dar_CORTHot) - (dar_ControlCold - dar_CORTCold)), 3)`) (@fig-deli A, B). Similarly, those assigned to 'Blue' were not afected by CORT (Control - CORT = `r format_dec(mean(c(dab_ControlCold - dab_ControlHot)) - mean(c(dab_CORTCold, dab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(dab_ControlCold - dab_ControlHot) - c(dab_CORTCold, dab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(dab_ControlHot, dab_CORTHot)) - mean(c(dab_ControlCold, dab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(dab_ControlHot, dab_CORTHot) - c(dab_ControlCold, dab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(dab_ControlHot - dab_CORTHot) - mean(dab_ControlCold - dab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((dab_ControlHot - dab_CORTHot) - (dab_ControlCold - dab_CORTCold)), 3)`) (@fig-deli C, D).

```{r, fig-deli}
#| label: fig-deli
#| fig.cap: "Results for _Lampropholis delicata_ for both colour groups "red" (A,B) and "blue" (C, D). Panels A and C show the predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions. The different colours indicate the different treatments. Panels B and D show the distribution of the estimates of slopes per each treatment. The x-axis represents the slope estimate, and in the y-axis are the density of the estimates. The different colours indicate the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# First step, create the dfs for all models
## Red
fig_dar_AC_df <- df_plotAC("deli_red")
fig_dar_BD1_df <- df_plotBD1("deli_red")
fig_dar_BD2_df <- df_plotBD2("deli_red")
## Blue
fig_dab_AC_df <- df_plotAC("deli_blue")
fig_dab_BD1_df <- df_plotBD1("deli_blue")
fig_dab_BD2_df <- df_plotBD2("deli_blue")
#
# Second step, create the plots
fig_dar <- plotting(sp = "deli", col = "red", df_prob = fig_dar_AC_df, df_violin = fig_dar_BD1_df, df_points = fig_dar_BD2_df)
fig_dab <- plotting(sp = "deli", col = "blue", df_prob = fig_dab_AC_df, df_violin = fig_dab_BD1_df, df_points = fig_dab_BD2_df)
#
# Third step, merge plots
fig_deli <- plot_grid(fig_dar, fig_dab, ncol = 1) +
  theme(plot.margin = margin(1, 1, 1.5, 1, "cm")) +
  annotate("text", x = 0.5, y = 0.985, label = "Lampropholis delicata", size = 4.5, color = "black", fontface = "italic")
ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/fig_deli.png")
```

In _L. guichenoti_, we did not find any significant differences between hormones (Control - CORT = `r format_dec(mean(c(gar_ControlCold - gar_ControlHot)) - mean(c(gar_CORTCold, gar_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gar_ControlCold - gar_ControlHot) - c(gar_CORTCold, gar_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gar_ControlHot, gar_CORTHot)) - mean(c(gar_ControlCold, gar_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gar_ControlHot, gar_CORTHot) - c(gar_ControlCold, gar_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gar_ControlHot - gar_CORTHot) - mean(gar_ControlCold - gar_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gar_ControlHot - gar_CORTHot) - (gar_ControlCold - gar_CORTCold)), 3)`) for those assigned to the 'Red' group (@fig-guich A, B); and we did not find any significant effect of hormone (Control - CORT = `r format_dec(mean(c(gab_ControlCold - gab_ControlHot)) - mean(c(gab_CORTCold, gab_CORTHot)), 3)`, p~mcmc~ `r format_p(pmcmc(c(gab_ControlCold - gab_ControlHot) - c(gab_CORTCold, gab_CORTHot)), 3)`), temperature (Hot - Cold = `r format_dec(mean(c(gab_ControlHot, gab_CORTHot)) - mean(c(gab_ControlCold, gab_CORTCold)), 3)`, p~mcmc~ `format_p(pmcmc(c(gab_ControlHot, gab_CORTHot) - c(gab_ControlCold, gab_CORTCold)), 3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean(gab_ControlHot - gab_CORTHot) - mean(gab_ControlCold - gab_CORTCold), 3)`, p~mcmc~ `r format_p(pmcmc((gab_ControlHot - gab_CORTHot) - (gab_ControlCold - gab_CORTCold)), 3)`) for those assigned to 'Blue' (@fig-guich C, D).
